Variation in gaze understanding across the life span: A process-level perspective

### 2023-06-23 paper/manuscript.Rmd
start working on modeling section

Task design, data collection, and sample sizes were pre-registered: https://osf.io/r3bhn. The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl. No. 2021_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology. The research adheres to the legal requirements of psychological research with children in Germany. Data were collected between May and August 2021.

@@

Data of children was collected in kindergartens located in Leipzig, Germany. The children within each kindergarten were recruited via an internal database, where each parent priorly consented to child development studies. 
Adults were recruited over *Prolific*  [@palan2018prolific].

Since developmental change was minimal in our adult sample (see Lifespan study) and the cognitive models were computationally heavy, we decided to only include the first 50 adults that completed the study.

## Procedure
As in the previous study, participants completed the continuous version of the TANGO [@prein2022tango]. Children were tested in a quiet room in their kindergarten, while an experimenter guided the child through the study on a tablet.

@@

@@

@@

Our computational cognitive model assumes that the ability to engage in vector estimation is a crucial component of mastering gaze understanding. In this study, we sought to inquire whether there are any other cognitive processes outside vector-following that constitute gaze understanding. We aimed to assess whether there are exclusively task-specific processes at hand or whether gaze understanding recruits a general social-cognitive ability that is shared among other social-cognitive tasks.

First, we aimed at isolating the vector-following part of the gaze understanding task. For this, we designed a new non-social vector estimation task that shared all crucial design features of the understanding task. Additionally, we administered a ToM task battery, comprising 4 tasks from the ToM scale by Wellman and Liu (2004) and two additional perspective-taking tasks.

Our reasoning was that the gaze understanding task shares task demands with the non-social vector estimation task, while it shares its social context with the ToM tasks. This way, we can disentangle which components comprise gaze understanding. In this way, we can find out what contribution each component makes to explain gaze understanding.

@@

Testing took place in kindergartens in Leipzig, Germany. The sample consisted of `r magnet_sample$n_total` children (mean age = `r magnet_sample$age_mean` years, SD = `r magnet_sample$age_sd`, range = `r magnet_sample$age_min` - `r magnet_sample$age_max`, `r magnet_sample$n_females` girls).

@@

Children were tested in a quiet room in their kindergarten. An experimenter guided the child through the study. Since our research questions related to individual differences and we wanted maximum control of extraneous participant variables, we employed a within-subjects design. All participants performed the following tasks in a fixed order: (1) non-social vector estimation task, (2) ToM task battery, (3) gaze understanding task. Several reasons motivated the decision. First, we decided for a fixed order to be able to compare participant's performance straight-forwardly with each other. Second, to increase participant engagement and decrease fatigue or fuzziness, we switched from a tablet task, to tasks with personal interaction, back to a tablet task. Third, we showed the non-social vector estimation task before the gaze understanding task, so that participants would not be biased to interpret the presented stimuli as "eye- / "agent-like".

@@

Modeling the setup and structure of the previously applied gaze understanding task, we designed a non-social vector estimation task. This task was also presented as a webapp and made use of the concept of magnetism. The setup looked as follows. On the upper part of the screen, there was a tube with a gearwheel, located in a circular window. On the floor, there laid a magnet. The magnet then got switched on (making a cartoon-like sound), whereupon the gearwheel moved towards the magnet. The gearwheel moved in a way that its center aligned with the center of the magnet. Participants were then asked to locate the magnet. Access to the magnet's true location was manipulated by a wooden wall: participants either had full, partial, or no visual access to the true magnet location. When no information about the magnet location was accessible, participants were expected to use the gearwheel inside the window as a non-social cue to locate the magnet.

As in the TANGO, there were three different trial types depending on the visual access to the true magnet location. In the touch training, participants had full visual access to the magnet's location (i.e., no wooden wall). In familiarization trials, participants had partial visual access, since the wooden wall was moved in front of the target after the magnet's location was already visible. In test trials, participants have no visual access to the magnet location, because the wall covers the magnet from the beginning of the trial.

Children received 19 trials with one touch training, two familiarization trials, and 16 test trials each. The first trial of each type comprised a voice-over description of the presented events. We conducted our analysis with 15 test trials, excluding the touch, familiarization, and voice-over trials. The outcome variable was imprecision, defined as the absolute difference between the magnet's x coordinate and the x coordinate of the participant's click. Magnet coordinates were generated as follows. The full width of the screen was divided into ten bins. Each bin occurred equally often, while the same bin could occur in two consecutive trials. Exact coordinates within each bin were randomly generated.

@@

We administered four tasks from the @wellman2004scaling Theory of Mind scale. We excluded three tasks: the Diverse Desires task in order to avoid ceiling effects; and both tasks involving emotions (Belief Emotion and Real-Apparent Emotion), as we aimed at assessing the "cold, cognitive" (as compared to the "emotional") aspects of social cognition. Instead, we added two perspective-taking level-2 tasks [@flavell1981development; @flavell1981younga], with the aim of increasing the task battery's difficulty. See Supplements for further detail. The dependent variable was the aggregate score of all solved ToM tasks. In an exploratory analysis, we investigated if gaze understanding was more strongly associated with the two perspective-taking tasks compared to the other ToM tasks, as perspective-taking seems most closely theoretically related to gaze understanding (i.e., in both cases the participant is asked to judge another person's point of view).

@@

Children were tested on a tablet. As in the two previously reported studies, we presented children with the continuous version of the TANGO [@prein2022tango]. 
To accentuate the social aspect of the gaze understanding task, we exchanged the animal agents (used in the previous two studies) with human faces, which were modeled after the local population in appearance. This further highlighted the contrast to the non-social vector estimation task. We had already created these stimuli for another project focusing on cross-cultural similarities in gaze understanding (https://osf.io/tdsvc). [^1]

@@

Furthermore, to estimate which components contribute to gaze understanding, we conducted a model comparison with GLMMs predicting the mean imprecision in gaze understanding by age, non-social vector estimation, the ToM aggregate score, or the aggregate of the two perspective-taking tasks (subset of ToM battery; example of model notation in `R: tango_mean ~ age_centered + magnet_scaled + perspective_scaled`). The outcome variable was modeled by a lognormal distribution. With this analysis, we wanted to assess whether the ToM aggregate score or the singled-out perspective-taking score added additional explanatory value when predicting the gaze understanding score.

@@

Gaze understanding and perspective-taking showed a *Spearman* correlation coefficient of $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`], while non-social vector estimation and perspective-taking showed a correlation of $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`]. According to the Williams' test, these two correlations did not differ significantly from each other, *t*(`r magnet_williamsttest_perspective$parameter`) = `r round(magnet_williamsttest_perspective$statistic, 2)`, *p* = `r round(magnet_williamsttest_perspective$p.value, 2)`.

Our model comparison revealed that gaze understanding was best predicted by a model including non-social vector estimation ($\beta$ = `r fixef(magnet_model)["magnet_scaled", "Estimate"]`, 95% CrI [`r fixef(magnet_model)["magnet_scaled", "Q2.5"]`; `r fixef(magnet_model)["magnet_scaled", "Q97.5"]`]) and perspective-taking ($\beta$ = `r fixef(magnet_model)["perspective_scaled", "Estimate"]`; 95% CrI [`r fixef(magnet_model)["perspective_scaled", "Q2.5"]`, `r fixef(magnet_model)["perspective_scaled", "Q97.5"]`]), even when controlling for age ($\beta$ = `r fixef(magnet_model)["age_centered", "Estimate"]`, 95% CrI [`r fixef(magnet_model)["age_centered", "Q2.5"]`, `r fixef(magnet_model)["age_centered", "Q97.5"]`]).

@@

(ref:figlab4) **Components of gaze understanding**

@@

In previous work, we could establish that the TANGO is suited as an individual differences measure [@prein2022tango]. Capturing meaningful variability in performance is a crucial task feature when we are interested in revealing the relationship between different cognitive abilities.

It seems noteworthy to point out that lower correlations between ToM skills and gaze understanding could be grounded in the design features of the applied ToM tasks. The tasks we used to measure ToM skills were not designed to capture individual differences: they rely on an aggregate score of dichotomous measures. These sum scores can only capture limited variance, which may obscure potential correlations. However, since these tasks are the gold standard in the social-cognitive literature and continuous measures with satisfying psychometric properties are, to the best of our knowledge, still scarce, we nonetheless relied on them in this study. The development of new measures to capture individual differences in social-cognitive abilities like false-belief understanding seems desirable and essential to move this line of research further.

>>>>

In a previous study, we have shown that the inter-individual variation in gaze understanding is reliable (@prein2022tango).
Now, we asked ourselves what varies between participants on a process-level and how this changes with age.
To answer this question, we aimed to formalize the process of gaze understanding in a computational cognitive model.
The model seeks to explain how participants solve the TANGO task.

Computational modeling frameworks allow researcher to establish mechanistic explanations of psychological phenomena and form testable predictions [@grahek2021anatomy].
As formal, mathematical accounts of the psychological process in question, they force researchers to accurately and comprehensively state all underlying assumptions [@simmering2010dialogue].
In addition, models can be used to simulate and predict behavior as it would be expected in novel experimental manipulations.
This can then in turn be compared to empirically observed behavior and can, for example, demonstrate assumptions of the model to be false.

The model assumes that participants estimate the agent's eye center and observe the current location of the pupil center.
These two point estimates are then used to calculate a vector that points towards the attentional focus of the agent.
Our model assumes that participants sample from a distribution around the true gaze vector.
Individual differences could now be explained as more narrow or wider distribution around the true gaze vector (i.e., amount of deviation).
This could represent participants' level of uncertainty in estimating the agent's attentional focus: the wider the distribution around the true gaze vector, the less precise participants estimate the focus of attention.
This is the key parameter in our model: this so-called inferential component describes how accurately the participant infers the attentional focus based upon the state of the agent's pupil.

However, participants who are very imprecise in locating the attentional focus of the agent could be less likely to make use of the eye information in the first place.
To accomodate this, we created an alternative model that estimates the probability that a participant engages in random guessing.

With this approach, we can formalize whether (A) a participant makes use of the available gaze information at all, and (B) how accurate they are, if they do pay attention to the agent's eyes.
We expect a dual developmental process.
The older children get, the more likely they are to use the gaze cues and the more precise they get in doing so.

The geometry of the estimated gaze vector and the sampling of a distribution around this vector lead to interesting, testable group-level predictions.
As the pupil location varies, a fixed amount of uncertainty about the eye angle corresponds to a varying amount of uncertainty in the estimated focus of attention (i.e., the target location).
This could be thought of as a "headlight distribution": when the agent's eye gaze is directed centrally to the ground in front of them, the distribution from which participants sample is comparatively more narrow then when the agent's eye gaze is directed to the side.
A similar phenomenon can be observed when you direct a torch light straight onto the ground or when you direct it at a further distance away from you.
It leads the model to predict that our trials vary in difficulty: participants' clicks should be more imprecise, the further out the target x coordinate is.

Task design, data collection, and sample sizes were pre-registered: <https://osf.io/r3bhn>.
The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl. No. 2021_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
The research adheres to the legal requirements of psychological research with children in Germany.
Data were collected between May and August 2021.

@@

Data of children was collected in kindergartens located in Leipzig, Germany.
The children within each kindergarten were recruited via an internal database, where each parent priorly consented to child development studies.
Adults were recruited over *Prolific* [@palan2018prolific].
Since developmental change was minimal in our adult sample (see Lifespan study) and the cognitive models were computationally heavy, we decided to only include the first 50 adults that completed the study.

As in the previous study, participants completed the continuous version of the TANGO [@prein2022tango].
Children were tested in a quiet room in their kindergarten, while an experimenter guided the child through the study on a tablet.
Adults participated online.

@@

Our cognitive model attempts to explain the behavior of participants as being generated by one of two possible approaches.
At each trial, a weighted coin toss determines whether the participant solves the task by \"guessing\" (sampling a clicking coordination from a uniform distribution over all possible coordinates) or by applying a gaze following model described below.
Each participant has their own \"guessing probability\", determining the mixture of strategies they use.
These per-participant parameters are modeled as having a Beta distribution over the population of participants.

Our proposed gaze understanding model is a simplification of an originally three-component model, which consisted of: (1) a perceptual component, whereby the participant produces a noisy observation of the angle of each of the agent's eyes, (2) an inferential component, whereby the participant produces an estimate of the coordinate the agent is looking at based on the above noisy observations of eye angles and a model of how agents direct their eyes relative to where they are looking, and (3) a motor component, whereby the participant samples a location to click at from a distribution centered around the above estimate of where the agent is looking.
Simulation studies suggested it was difficult to disentangle the independent noise terms from these three components and so the model was simplified to include only the inferential component

In the inferential component, the participant assumes that the agent\'s attention is focused on a single point coordinate and that the agent\'s left and right eyes are positioned by sampling (independently for each eye) eye angles from Normal distributions centered on the unique angle such that a line subtended from the center of the agent\'s eye through the center of its pupil will meet the attentional focal point (i.e. the modal behavior is to direct both eyes directly toward the focal point).
The standard deviation of these distributions (equal for each eye) is a parameter that varies per participant, with higher values increasing the expected imprecision.
When interpreted strictly as a model of inferring attentional focus, this standard deviation corresponds to the participant\'s assumptions about how wide an area of the agent\'s visual field their attention occupies.

Because of the geometry of the situation (where a fixed amount of uncertainty about the agent\'s eye angle corresponds to a varying amount of uncertainty in the underlying point of attention as the eye angle varies), and because the participant integrates information from two eyes, the resulting posterior distribution (which the participant\'s mouse click is modeled as a sample from) does not belong to a standard parametric family, but can be easily numerically approximated as part of the inference process.

We will compare this model against two models which represent alternatives about how participants' responses are generated.
The \"random guessing\" model simply assumes that participants ignore the agent's gaze and randomly click on the screen (cf. coin toss, sampling a coordination from a uniform distribution over all possible coordinates).
The \"motor noise\" model assumes that participants have no uncertainty about where the agent is looking but that their responses (clicks on the screen) come with a small amount of random noise (cf. motor component of our originally proposed model).
We will then directly compare the three models via BayesFactors computed based on the marginal log-likelihood of the data under each model.
The models make different predictions about how participants\' clicks will be distributed for different locations of the target.
We will visualise and evaluate these differences using correlations between the model predictions and the data.

@@

A big advantage of using a computational modeling framework is that it can disentangle where people's errors come from.
Our computational model can explain what varies between precise and imprecise individuals.
There are two sources of errors: (1) do you actually use the eye gaze information?
and (2) how accurate are you at estimating the focus point when you do pay attention to the agent's eyes?
This way, we can track developmental changes in gaze understanding in a more fine-tuned way.

In addition, our model was able to recover "signature patterns" in the data.
Both the model predictions and the actual raw data show that precision levels drop as the agent's gaze moves further away from the center.
Future research could use this signature in the data as evidence whether diverse communities employ the same mechanism to solve the task.

@@

Our computational cognitive model assumes that the ability to engage in vector estimation is a crucial component of mastering gaze understanding.
In this study, we sought to experimentally isolate the physical vector estimation component.
In addition, we inquired whether there are any other cognitive processes outside the vector estimation that constitute gaze understanding.
We aimed to assess whether there are exclusively task-specific processes at hand or whether gaze understanding recruits a general social-cognitive ability that is shared among other social-cognitive tasks.

First, we aimed to isolate the vector estimation component of the gaze understanding task.
We designed a new non-social vector estimation task that shared all crucial design features of the gaze understanding task.
Second, we assessed children's social-cognitive abilities by administering a ToM task battery, comprising four tasks from the ToM scale by Wellman and Liu (@wellman2004scaling) and two additional perspective-taking tasks [@flavell1981development; @flavell1981younga].

Our reasoning was that the gaze understanding task shares task demands with the non-social vector estimation task, while it shares its social context with the ToM tasks.
This way, we can disentangle what components comprise gaze understanding.

@@

Testing took place in kindergartens in Leipzig, Germany.
The sample consisted of `r magnet_sample$n_total` children (mean age = `r magnet_sample$age_mean` years, SD = `r magnet_sample$age_sd`, range = `r magnet_sample$age_min` - `r magnet_sample$age_max`, `r magnet_sample$n_females` girls).
Information on individual socio-economic status was not formally recorded.
Children in our sample live in an industrialized, urban Central-European city with approximately 600,000 inhabitants.
Households often consist of nuclear families with few household members.
The majority of families in our data base come from mainly mid to high socio-economic backgrounds with high levels of parental education.

@@

Children were tested in a quiet room in their kindergarten.
An experimenter guided the child through the study.
Since our research questions related to individual differences and we wanted maximum control of extraneous participant variables, we employed a within-subjects study design.
All participants performed the following tasks in a fixed order: (1) non-social vector estimation task, (2) ToM task battery, (3) gaze understanding task.
Several reasons motivated this decision.
First, we decided on a fixed order to be able to compare participants' performance straight-forwardly with each other.
Second, to increase participant engagement and decrease fatigue or fuzziness, we switched from a tablet task to tasks with personal interaction back to a tablet task.
Third, we showed the non-social vector estimation task before the gaze understanding task so that participants would not be biased to interpret the presented stimuli as "eye- /"agent-like".

@@

Modeling the setup and structure of the previously applied gaze understanding task, we designed a non-social vector estimation task.
This task was also presented as a webapp on a tablet and made use of the concept of magnetism.
The setup looked as follows.
On the upper part of the screen, there was a tube with a gearwheel located in a circular window.
On the floor, there lay a magnet.
The magnet then got switched on (making a cartoon-like sound), whereupon the gearwheel moved towards the magnet.
The gearwheel moved in a way that its center aligned with the center of the magnet, while staying inside the circular window.
Participants were then asked to locate the magnet.
Access to the magnet's true location was manipulated by a wooden wall: participants either had full, partial, or no visual access to the true magnet location.
When no information about the magnet location was accessible, participants were expected to use the gearwheel inside the window as a non-social cue to locate the magnet.

As in the TANGO, there were three different trial types depending on the visual access to the true magnet location.
In full visual access trials, the magnet's location was presented without impediment (i.e., no wooden wall).
In partial visual access trials, the wooden wall was moved in front of the target after the magnet's location had already been visible.
In test trials, participants had no visual access to the magnet's location because the wall covered the magnet from the beginning of the trial.

Children received 19 trials with one full visual access trial, two partial visual access trials, and 16 test trials.
The first trial of each type comprised a voice-over description of the presented events.
We conducted our analysis with 15 test trials (excluding the voice-over trial).
The outcome variable was imprecision, defined as the absolute difference between the magnet's x coordinate and the x coordinate of the participant's click.
Magnet coordinates were generated as follows.
The full width of the screen was divided into ten bins.
Each bin occurred equally often, while the same bin could occur in two consecutive trials.
Exact coordinates within each bin were randomly generated.

@@

We administered four tasks from the @wellman2004scaling Theory of Mind scale.
We excluded three tasks: the Diverse Desires task in order to avoid ceiling effects; and both tasks involving emotions (Belief Emotion and Real-Apparent Emotion), as we aimed at assessing the "cold, cognitive" (as compared to the "emotional") aspects of social cognition.
Instead, we added two perspective-taking level-2 tasks [@flavell1981development; @flavell1981younga].
We added the perspective-taking tasks (1) with the aim of increasing the task battery's difficulty, and (2) since we hypothesized that perspective-taking would rely on similar mechanisms than gaze understanding.
The dependent variable was the aggregate score of all solved ToM tasks (see Supplements for further detail).
In an exploratory analysis, we investigated if gaze understanding was more strongly associated with the two perspective-taking tasks compared to the other ToM tasks, as perspective-taking seems most closely theoretically related to gaze understanding (i.e., in both cases the participant is asked to judge another person's point of view).

@@

As in the two previously reported studies, we presented children with the continuous version of the TANGO [@prein2022tango].
To accentuate the social aspect of the gaze understanding task, we exchanged the animal agents (used in the previous two studies) with human faces, which were modeled after the local population in appearance (already created for another project on cross-cultural similarities in gaze understanding (<https://osf.io/tdsvc>)).
This further highlighted the contrast (i.e., social vs. non-social context) to the non-social vector estimation task.[^1]

@@

Furthermore, to estimate which components best explain the gaze understanding score, we conducted a model comparison with GLMMs predicting the mean imprecision in gaze understanding by age, imprecision in non-social vector estimation, the ToM aggregate score, or the aggregate of the two perspective-taking tasks (subset of ToM battery; example of model notation in `R: tango_mean ~ age_centered + magnet_scaled + perspective_scaled`).
We wanted to assess whether the ToM aggregate score or the singled-out perspective-taking score added additional explanatory value when predicting the gaze understanding score.
The outcome variable was modeled by a lognormal distribution.

@@

Gaze understanding and perspective-taking showed a *Spearman* correlation coefficient of $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`], while non-social vector estimation and perspective-taking did not correlate, $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`].
According to the Williams' test, these two correlations did not differ significantly from each other, *t*(`r magnet_williamsttest_perspective$parameter`) = `r round(magnet_williamsttest_perspective$statistic, 2)`, *p* = `r round(magnet_williamsttest_perspective$p.value, 2)`.

Our model comparison revealed that gaze understanding was best predicted by a model including non-social vector estimation ($\beta$ = `r fixef(magnet_model)["magnet_scaled", "Estimate"]`, 95% CrI [`r fixef(magnet_model)["magnet_scaled", "Q2.5"]`; `r fixef(magnet_model)["magnet_scaled", "Q97.5"]`]) and perspective-taking ($\beta$ = `r fixef(magnet_model)["perspective_scaled", "Estimate"]`; 95% CrI [`r fixef(magnet_model)["perspective_scaled", "Q2.5"]`, `r fixef(magnet_model)["perspective_scaled", "Q97.5"]`]), even when controlling for age ($\beta$ = `r fixef(magnet_model)["age_centered", "Estimate"]`, 95% CrI [`r fixef(magnet_model)["age_centered", "Q2.5"]`, `r fixef(magnet_model)["age_centered", "Q97.5"]`]).
See Supplements for further detail of the model comparison.

@@

(ref:figlab4) **Components of gaze understanding.** (A) Correlations between gaze understanding, physical vector estimation, ToM, and perspective-taking. Dots show the correlation coefficients, while error bars represent 95% CIs. (B) Influence of perspective-taking and physical vector estimation on gaze understanding. The graph show the posterior distributions for the respective predictor. Black dots represent means, thicker black lines 80% CrI and thinner black lines 95% CrI.

@@

By carefully isolating physical vector estimation experimentally, we could show that gaze understanding does indeed, to a certain degree, rely on this component.
This is in line with our computational cognitive framework that assumes vector calculations on a process-level.
However, physical vector estimation alone did not suffice to explain gaze understanding.
In addition, perspective-taking proved to be a relevant social-cognitive ability.

In previous work, we could establish that the TANGO is suited as an individual differences measure [@prein2022tango].
Capturing meaningful variability in performance is a crucial task feature when we are interested in revealing the relationship between different cognitive abilities.
Importantly, the tasks we used to measure ToM abilities were not designed to capture individual differences: they relied on an aggregate score of dichotomous measures.
These sum scores can only capture limited variance, which may obscure potential correlations.
However, since these tasks are the gold standard in the social-cognitive literature and continuous measures with satisfying psychometric properties are, to the best of our knowledge, still scarce, we nonetheless relied on them in this study.
It seems noteworthy to point out that lower correlations between ToM abilities and gaze understanding could be grounded in the design features of the applied ToM tasks.
We already stated this concern in the Pre-registration (<https://osf.io/xsqkt>).
The development of new measures to capture individual differences in social-cognitive abilities like false-belief understanding seems desirable and essential to move this line of research further.
